---
title: "01_Generate-Split"
author: "Junyi Chu"
date: '2022-04-10'
output:
  html_document:
    df_print: paged
    code_folding: hide
---

This notebook generates the train/test split for already annotated videos from the Lookit Physics project (prefphys). Specifically, this generates two tables:

- A **participant table** listing each participant, their train/test assignment, and some demographic information used to make the split (age, sex, race)
- A **video table** listing video sessions (might be multiple per participant) and matched annotation file(s). 

This is a work in progress. Work flow:

1. Setup (import files, some checks)
2. Generate dataframe containing information about each participant
3. Conduct sampling procedure to assign participants to train/test, with some manual adjustments as needed
4. Report statistics of participants assigned to train/test.
5. Generate desired output tables and export as csv

The R notebook "02_Move-files-for-QI.Rmd" then copies appropriate video and annotation files into the Dropbox folder for QI engineers.

# Setup 

Do some basic R setup, import packages, set random seed.

```{r setup, include=F}
# clear memory and run garbage collector
rm(list = ls()); gc()
# Load packages
if(!require("pacman")) install.packages("pacman")
pacman::p_load('tidyverse', 'stringr', 'rstudioapi', 'knitr')
# set default chunk options 
knitr::opts_chunk$set(
	fig.height = 4,
	fig.width = 6,
	message = FALSE,
	warning = FALSE
)
# Random seed
set.seed(12341)

#lookitdir <- "/Volumes/LookitVideo/PrefPhys-coding/"
lookitdir <- "/Users/junyichu/Dropbox (MIT)/2 NOW/2018 Physics/Data/"
qidir <- "/Users/junyichu/Dropbox (MIT)/2 NOW/2018 Physics/Videos for QI/"
```

This notebook takes as input Session data (dates, age, etc) and Participant demographic data (from Lookit). For now, we use original session uuids, lookit user ids, etc. Eventually we want to use deidentified IDs.

```{r import, include=F}
# List of video files available for scientific use
df.videos<- read_csv(paste0(lookitdir,"Video-list-all.csv")) %>%
  filter(privacy %in% c("scientific", "public"))

# For those children, annotation summary
df.kids <- read_csv(paste0(lookitdir,"Annotation-list-by-child_share.csv")) %>%
  mutate(childID = ifelse(str_detect(childID, '\\.'),
                    str_sub(childID,-5,-1),
                    childID))
df.kids_demo <- 
  read_csv(paste0(lookitdir,'raw participant data/prefphys_participants_data-identifying.csv')) %>% 
  select(-coded_1, -coded_2, -coded_0, -childid.video, -age_at_birth,
         -parent.age, -parent.child_birthdays,
         -parent.gender, -parent.date_created,
         -parent.former_lookit_annual_income,
         -parent.lookit_referrer, -parent.number_of_children,
         -parent.number_of_guardians_explanation,
         -parent.number_of_guardians,
         -parent.income) %>% # unused for now
  mutate(child = ifelse(str_detect(child, '\\.'),
                    str_sub(child,-5,-1),
                    child),
                    parent.race.NA = parent.race_identification=="[]" | is.na(parent.race_identification),
         parent.race.white=str_detect(parent.race_identification,"white|White"),
         parent.race.asian=str_detect(parent.race_identification,"asian|Asian"),
         parent.race.black=str_detect(parent.race_identification,"black|Black"),
         parent.race.hispanic=str_detect(parent.race_identification,"hisp|Hisp"),
         parent.race.mideastnaf=str_detect(parent.race_identification,"Middle|mideast"),
         parent.race.hpi=str_detect(parent.race_identification, "hawaiian|Hawaiian"),
         parent.race.native=str_detect(parent.race_identification, "native"),
         parent.race.other=str_detect(parent.race_identification, "other")) %>%
  mutate(parent.race.nonwhite=ifelse(parent.race.NA, NA,
                                  parent.race.asian|parent.race.black|
                                  parent.race.hispanic|parent.race.mideastnaf|
                                    parent.race.hpi|parent.race.native|parent.race.other))
# Session metadata (age, age rounded, gender, session date, video duration, mood)
df.sessions<- read_csv(paste0(lookitdir,'raw participant data/prefphys_sessions_metadata-identifiable.csv')) %>%
  select(-n_coders, -childid.video, -uuid.video,
         -created_on, -completedStudy) %>% # remove unnecessary identifiers
  mutate(mood.lastEat = as.numeric(mood.lastEat)/60) %>% # convert hms to minutes
  mutate(child = ifelse(str_detect(child, '\\.'),
                    str_sub(child,-5,-1),
                    child),
           child.ageSessionRounded = floor(child.ageSession)) # fix
    
```

Clean and add pilot demographic data

```{r}
df.pilotkids <- read_tsv(paste0(lookitdir,"raw participant data/pilot_participants_data-identifying.tsv")) %>%
  rename(uuid=shortId, 
         child=child.profileId, 
         race_identification = household_race_identification,
         state = state_location) %>%
    mutate(child = ifelse(str_detect(child, '\\.'),
                    str_sub(child,-5,-1),
                    child)) %>%
  rename_with(.fn = ~paste0("parent.", .x),
    .cols=languages_spoken:density) %>%
    mutate(studyid="57bc591dc0d9d70055f775db",
           nsessions_avail=1,
           nsessions_coded=1,
           child.age.min=floor(ageRegistration),
           child.age.max=floor(ageRegistration),
           parent.annual_income = as.character(parent.annual_income),
           # mutate race
           parent.race.NA = parent.race_identification=="[]" | is.na(parent.race_identification),
         parent.race.white=str_detect(parent.race_identification,"white|White"),
         parent.race.asian=str_detect(parent.race_identification,"asian|Asian"),
         parent.race.black=str_detect(parent.race_identification,"black|Black"),
         parent.race.hispanic=str_detect(parent.race_identification,"hisp|Hisp"),
         parent.race.mideastnaf=str_detect(parent.race_identification,"Middle|mideast"),
         parent.race.hpi=str_detect(parent.race_identification, "hawaiian|Hawaiian"),
         parent.race.native=str_detect(parent.race_identification, "native"),
         parent.race.other=str_detect(parent.race_identification, "other")) %>%
  mutate(parent.race.nonwhite=ifelse(parent.race.NA, NA,
                                  parent.race.asian|parent.race.black|
                                  parent.race.hispanic|parent.race.mideastnaf|
                                    parent.race.hpi|parent.race.native|parent.race.other))

# Combine! 
common_cols <- intersect(colnames(df.kids_demo), colnames(df.pilotkids))

df.demo <- bind_rows(
  df.kids_demo, # keep all
  df.pilotkids[common_cols]
)
```

Clean and add pilot session data


```{r}
# Add PILOT to session metadata & child demographic data
# 
df.sessions.pilot <- read_csv(paste0(lookitdir,"raw participant data/pilot_trials_data.csv")) %>%
  select(uuid=shortId, 
         child=child.profileId, 
         child.gender,
         child.ageSession=ageRegistration,
         consentnotes, usable,
         privacy.exit=exit.survey.useOfMedia,
         privacy.databrary = exit.survey.databraryShare,
         video.nVideosExpected = nVideosExpected,
         video.nVideosFound = nVideosFound,
         video.expectedDuration = expectedDuration,
         video.actualDuration = actualDuration,
         starts_with("mood.survey")) %>%
  unique() %>%
  rename_with(~str_replace(., "mood.survey.", "mood.")) %>%
  rename(mood.minsToNextNap = mood.nextNap,
         mood.minsSincePrevNap = mood.napWakeUp) %>%
  mutate(
    child.ageSessionRounded = floor(child.ageSession),
    studyid = "57bc591dc0d9d70055f775db",
    child = str_sub(child,-5,-1),
    child.gender = tolower(substr(child.gender, 1, 1)),
    video.privacy = case_when(
      is.na(privacy.exit) ~ "private.local",
      privacy.exit == "private" &
        privacy.databrary == "yes" ~ "private.databrary",
      privacy.exit == "private" &
        privacy.databrary == "no" ~ "private.local",
      privacy.exit == "scientific" &
        privacy.databrary == "yes" ~ "scientific.databrary",
      privacy.exit == "scientific" &
        privacy.databrary == "no" ~ "scientific.local",
      privacy.exit == "public" &
        privacy.databrary == "yes" ~ "public.databrary",
      privacy.exit == "public" &
        privacy.databrary == "no" ~ "public.local"
    )
  )

# Combine! Ignore non-shareable
df.sessions <- bind_rows(df.sessions, df.sessions.pilot) %>%
  filter(privacy.exit != "private")
```

Remove unnecessary tables
```{r}
rm(df.kids_demo, df.pilotkids, df.sessions.pilot, common_cols)
```

### Check missing

There are 12 videos from pilot study that we lack demographic informaion and session metadata for.

```{r include=FALSE}
# define "without" function, give me x without y
"%w/o%" <- function(x, y) x[!x %in% y]

# 3 have lookit session, but no video. These are OK
df.sessions %>% filter(uuid %in% (uuid %w/o% df.videos$videoID))

# 10 videos not in the pilot study list of included sessions, that's OK
df.videos %>% filter(videoID %in% (videoID %w/o% df.sessions$uuid))

# 0 videos from pilot study lack demographic data, that's OK
df.videos %>% filter(childID %in% (childID %w/o% df.demo$child))
```

# Participant dataframe

So generate the list of children we care about for icatcher purposes, which is we have (1) session data, (2) demographic data, and (3) video files

```{r include=FALSE}
child_list <- intersect(
  intersect(df.sessions$child, df.demo$child), 
  df.videos$childID)

df.videos.share <- df.videos %>% filter(childID %in% child_list)
df.demo.share <- df.demo %>% filter(child %in% child_list)
df.sessions.share <- df.sessions %>% filter(child %in% child_list,
                                      uuid %in% df.videos$videoID)
df.kids.share <- df.kids %>% filter(childID %in% child_list)

```

### Participant breakdown by study version:

Only includes scientific / private sessions. These all match, nice.

```{r}
# video
df.videos.share %>% count(childID, studyID) %>% count(studyID)
# shareable sessions
df.sessions.share %>% count(child, studyid) %>% count(studyid)
# kids
df.kids.share %>% count(studyID)
df.demo.share %>% count(studyid)
```

## Participant Table

We want the variables:

- age at session 1 (in months)
- gender (m/f)
- race (nonwhite yes, no, or NA)
- number of sessions / videos available
- number of videos coded
- country

```{r}
participants <- df.demo.share %>%
  select(studyid, child, child.gender, parent.race.white, parent.race.nonwhite) %>%
  mutate(child.gender = str_sub(child.gender, 1, 1),
         parent.race.nonwhite = factor(parent.race.nonwhite, 
                                          levels=c(FALSE, TRUE),
                                          labels=c("white only", "reported non-white"))) %>%
  left_join(df.kids.share, by=c(studyid='studyID', child='childID'))

videos <- df.videos.share %>% 
  left_join(df.sessions.share,
            by=c(studyID="studyid", childID="child", videoID="uuid",
                 privacy="privacy.exit")) %>%
  left_join(select(participants, studyid:parent.race.nonwhite),
            by=c(studyID="studyid", childID="child", 
                 child.gender='child.gender')) %>%
  rename(video.nTrialsExpected = video.nVideosExpected,
         video.nTrialsFound = video.nVideosFound) %>%
  mutate(n_coders=as.factor(3-is.na(coder1)-is.na(coder2)-is.na(coder3)),
         child.ageSessionRounded = ifelse(child.ageSession < 4, 4, child.ageSessionRounded)) # count the 3.97 month old as 4 months old

participants <- 
    videos %>% group_by(childID) %>% 
      summarise(child.age.min = min(child.ageSessionRounded),
            child.age.max = max(child.ageSessionRounded)) %>%
      right_join(participants, by=c(childID='child'))

# check consistency between the two tables
sum(participants$n_videos) == nrow(videos)
sum(participants$n_coded) == sum(!is.na(videos$coder1))
sum(participants$n_codedtwice) == sum(!is.na(videos$coder2))
```

In total, we have `r nrow(participants)` children contributing `r nrow(videos)` scientific/public level videos. 

Of these, `r sum(participants$n_coded)` videos have been coded. Of these, `r sum(participants$n_codedtwice)` are coded by two humans. The coded videos come from `r sum(participants$n_coded>0)` participants.

```{r}
videos %>% # plot
  filter(child.ageSession < 15) %>%
  ggplot(aes(y=reorder(childID, child.ageSessionRounded))) +
  geom_point(aes(x=child.ageSessionRounded, color=n_coders), alpha=0.5) +
  labs(x='Age (months)', y='Child', title='Data availability by age and race') +
  facet_grid(vars(parent.race.nonwhite)) +
  theme(axis.text.y=element_text(size = 5)) +
  scale_x_continuous(breaks=seq(4,14,1))+
  scale_color_manual(values=c("grey50", "blue", "forestgreen", "pink"))
```

## Age

We have some variability by age. The coded set reflects this distribution:

```{r}
participants %>%
  ggplot() +
  geom_bar(aes(x=child.age.min, fill=n_coded>0),
           color='black') +
  labs(title="Unique kids by age",
       x="Age (months) at first session",
       fill="Have 1+ annotations") +
  theme_bw()+
  theme(legend.position = c(.75, .95),
    legend.justification = c("left", "top")) +
  scale_x_continuous(breaks=seq(4,14,1))
```

Since each child contributes multiple sessions,we can look at overall dataset by session:

```{r}
videos %>% filter(child.ageSessionRounded<15) %>%
  arrange(-n_coders) %>%
  ggplot() +
  geom_bar(aes(x=child.ageSessionRounded, fill=as.factor(n_coders)),
           color='black')+
  scale_fill_manual(values=c("grey50", "blue", "forestgreen", "pink")) +
  scale_x_continuous(breaks=seq(4,14,1))+
  labs(title="Sessions by age", 
       x="Age (months)",
       fill="# Times coded") +
  theme_bw()+
  theme(legend.position = c(.75, .95),
    legend.justification = c("left", "top"))
```

Relatively speaking, 
```{r}
videos %>% filter(child.ageSessionRounded<15) %>%
  arrange(-n_coders) %>%
  ggplot() +
  geom_bar(aes(x=child.ageSessionRounded, fill=as.factor(n_coders)),
           color='black', position = position_fill(),
           width=)+
  scale_fill_manual(values=c("grey50", "blue", "forestgreen", "pink")) +
  scale_x_continuous(breaks=seq(4,14,1))+
  labs(title="Sessions by age", 
       x="Age (months)",
       fill="# Times coded") +
  theme(legend.position = c(.75, .95),
    legend.justification = c("left", "top"))
```

## Gender

```{r}
ggplot(participants, aes(x=child.gender, fill=n_coded>0)) +
  geom_bar(aes(x=child.gender, fill=n_coded>0),
           color='black') +
  labs(title="Unique kids by gender",
       x="Gender (female/male)",
       fill="Have 1+ annotations") +
  theme_bw()+
  theme(legend.position = c(.75, .95),
    legend.justification = c("left", "top"))
```

## Race

Participant count by race/ethnicity (white/nonwhite). This was a multi-select checkbox, and we actually have quite a few children who selected multiple options.

```{r eval=FALSE, include=FALSE}
# Table
addmargins(with(participants, table(parent.race.white, parent.race.nonwhite)))

#plot
df.demo.use %>% mutate(n_races =
                     parent.race.white+parent.race.asian+parent.race.black+parent.race.hispanic+
                     parent.race.mideastnaf+parent.race.hpi+parent.race.native+parent.race.other) %>%
  ggplot() + 
  geom_bar(aes(x=n_races, fill=parent.race.nonwhite), color="black") +
  labs(subtitle="Children, multiracial",y="Number of unique children",
       x="Number of races reported",
       fill="Reported non-white") +
  theme_bw() + 
    theme(legend.position = c(.7, .95),
    legend.justification = c("left", "top"))

```


Participants by race and coding status.

```{r}
#Table
addmargins(with(participants, 
                table(parent.race.nonwhite,n_coded>0)), 2)
#Plot
ggplot(participants, aes(x=parent.race.nonwhite, fill=n_coded>0)) +
  geom_bar()
```

# Sampling procedure

Let's bin ages every two months

```{r}
participants_ML <- participants %>% filter(n_coded>0) %>%
    mutate(child.age.bin = case_when(
    child.age.min <= 6 ~ "04-06mo",
    child.age.min <= 9 ~ "07-09mo",
    child.age.min <= 14 ~ "10-14mo"
  ))
```

Out of the **already coded**, we need a split for developing technical tools (at minimum, disjoint sets of babies - same babies NOT in both sets). Currently there are `r nrow(participants_ML)` unique infants with coded videos, consisting of:

- `r sum(participants_ML$studyid=="57bc591dc0d9d70055f775db")` unique infants from pilot set (each 1 video)
- `r sum(participants_ML$studyid!="57bc591dc0d9d70055f775db")` unique infants in non-pilot, already coded set

## Dataset statistics  {.tabset}

- Age (4 to 14 months old, divided into 3 intervals)
- Sex (female / male)
- Race (None or Any reported non-white racial identification)

There are 3x2x2 = 12 subgroups that we want evenly divided into train/test

### Mosaic plot 

Graph race, sex and age -- we want to split this into even sets.

```{r mosaic_all, include=TRUE}
library(ggmosaic)
ggplot(data = participants_ML) +
  #geom_mosaic(aes(x=product(child.age.bin, parent.race.nonwhite),
  #                fill=child.gender)) + 
  geom_mosaic(aes(x=product(child.age.bin, parent.race.nonwhite),
                  fill=child.gender,
              alpha=parent.race.nonwhite))+
  scale_alpha_manual(values =c(.9,.6)) +
  labs(x="Gender : Race", y="Age")+
    theme_mosaic()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

### Race

```{r, include=TRUE}
participants_ML %>% 
  count(parent.race.nonwhite) %>%
  mutate(prop = n/sum(n),
         target_n = n*.8)
```

### Age

Note that repeat sessions will be older in age, but still within 2 months of first session. 

```{r, include=T}
participants_ML %>% 
  count(child.age.bin) %>%
  mutate(prop = n/sum(n),
         target_n = n*.7)
```


### Sex

```{r, include=T}
participants_ML %>% 
  count(child.gender) %>%
  mutate(prop = n/sum(n),
         target_n = n*.7)
```

## Generate split

We follow procedure in [https://towardsdatascience.com/stratified-sampling-and-how-to-perform-it-in-r-8b753efde1ef](https://towardsdatascience.com/stratified-sampling-and-how-to-perform-it-in-r-8b753efde1ef)

```{r}
n_training_kids = round(.8*nrow(participants_ML))
n_test_kids = nrow(participants_ML) - n_training_kids
n_validation_kids = round(.1*n_training_kids)
```

We're targeting 20% for test (n= `r n_test_kids` kids) and 80% for training (n= `r n_training_kids`). Training set will be further divided into 10% for validation (`r n_validation_kids`). 

### First split into 80/20 train/test

```{r include=FALSE}
# Set seed
set.seed(2222)
# Make simplified dataset to sample from
d = participants_ML
n_sample = n_test_kids
generated = head(d,0)
dimensions = c("child.age.bin", "parent.race.nonwhite", "child.gender")
library(sqldf)
while (nrow(generated) < n_sample) {
  # For debug purposes
  cat(nrow(generated),"\n")
  flush.console()

  tmp = d

  # Calculate the histogram for each dimension
  # and select one value at a time, slicing the
  # original dataset according to its histogram
  for (i in 1:length(dimensions)) {

    colname = dimensions[i]
    if (class(d[[colname]]) %in% c("numeric") &&
        sum(d[[colname]] == as.integer(d[[colname]]),na.rm = TRUE) == 0
        ) {
      # Numerical variable. Histogram with Rice's Rule

      # If there are NA's, stratify on those

      na_count = sum(is.na(tmp[[colname]]))
      not_na_count = length(tmp[[colname]]) - na_count

      s = sample(c(0,1),prob = c(not_na_count,na_count),1)

      if (s == 0) {
        # Histogram stratification based on breaks calculated on the
        # population

        n_breaks = floor(2*sum(!is.na(d[[colname]]))**((1/3)))
        bar_size = (max(d[[colname]],na.rm = TRUE)-min(d[[colname]],na.rm = TRUE))/n_breaks

        breaks = sapply(0:n_breaks,function(i) {min(d[[colname]],na.rm = TRUE) + i*bar_size})

        h = hist(tmp[[colname]],breaks=breaks,plot = F)

        # Select one bar of the histogram according to the density
        bar_id  = sample(1:length(h$mids),prob = h$counts,1)

        bar_start = h$breaks[bar_id]
        bar_end = h$breaks[bar_id + 1]

        tmp = tmp[tmp[[colname]] >= bar_start & tmp[[colname]] < bar_end & !is.na(tmp[[colname]]),]
      } else {
        # NA
        tmp = tmp[is.na(tmp[[colname]]),]
      }

    } else {
      # Categorical variable

      # Histogram for the selected dimension
      aggr = as.data.frame(table(tmp[,colname],useNA="ifany"))
      names(aggr) = c("dim","count")

      # Generate a value according to the histogram
      generated_value = sample(aggr$dim,prob=aggr$count,1)

      # Slice the actual multivariate histogram in order to
      # take only records with the selected value on the
      # selected dimension
      if (!is.na(generated_value)) {
        tmp = tmp[tmp[[colname]] == generated_value & !is.na(tmp[[colname]]),]
      }
      else {
        tmp = tmp[is.na(tmp[[colname]]),]
      }

    }

  }

  # Once the procedure finishes, we get a bulk of records
  # with the same values of each dimension. Let's take
  # one of these records uniformly
  random_index = sample(1:nrow(tmp),1)
  new_record = tmp[random_index,]

  # Let's remove duplicates
  inserted_record = sqldf("select * from new_record except select * from generated")

  # Insert in the "train" data frame and repeat until desired sample size is reached
  generated = unique(rbind(generated,inserted_record))
}

# Save as a variable in the participants list
participants_ML <- participants_ML %>% 
  mutate(which.dataset = ifelse(
    childID %in% na.omit(generated$childID),
    "2_test","1_train"))
rm(tmp)
```

**Manual adjustment**

```{r}
# Work with a temporary table for manual adjustments
split0 <- participants_ML
table(split0$which.dataset)

## VIEW
# select(split0, childID,
#                            child.gender,
#                            child.age.bin,
#                            parent.race.nonwhite,
#                            which.dataset) %>%
#   arrange(child.age.bin, child.gender, parent.race.nonwhite, which.dataset) %>%
#   view()

## MANUAL ADJUSTMENT
split0$which.dataset[split0$childID %in% 
                           c("WIH7v", #4-6mo F nw
                             "09c87d6e-36c0-455d-812d-4576b1b0eefd", #7m M W
                             "196cf907-a938-441a-8734-92e5ae5e1890", #7m M W
                             "lVaOv"#10m M W)
                             )] <- "1_train"

split0$which.dataset[split0$childID %in% 
                           c("9b160510-da03-4228-b086-aba9552eb782", #4m M w
                             "0e44a3f3-c00f-4d0c-977b-a465175cddb9", #4m M nw
                             "MTBMm", #7m F W
                             "0a787312-132e-4358-9419-867703174245", #7m M NW
                             "H1Ree", #7m F W
                             "8f84d5ba-a074-451f-aca5-87ffa8298a47" #7m F NW
                             )] <- "2_test"

# Plot
ggplot(split0) +
    geom_mosaic(aes(x=product(child.age.bin, child.gender),
                    fill=child.gender,
                    alpha=which.dataset))+
    facet_wrap(.~parent.race.nonwhite, drop = T)+
    scale_alpha_manual(values =c(.9,.6)) +
    theme_mosaic()+
    theme(axis.text.x = element_text(angle = 90))

# Assign
participants_ML<- split0
testkids <- participants_ML %>% 
  filter(which.dataset=="2_test")
trainkids <- participants_ML %>% 
  filter(which.dataset=="1_train")

```

### Split train into train/validate

```{r sample, include=FALSE}
# Set seed
set.seed(2222)
# Sample from training set
d = trainkids
generated2 = head(d,0)
dimensions = c("child.age.bin", "parent.race.nonwhite", "child.gender")
while (nrow(generated2) < n_validation_kids) {
  # For debug purposes
  cat(nrow(generated2),"\n")
  flush.console()

  tmp = d

  # Calculate the histogram for each dimension
  # and select one value at a time, slicing the
  # original dataset according to its histogram
  for (i in 1:length(dimensions)) {

    colname = dimensions[i]
    if (class(d[[colname]]) %in% c("numeric") &&
        sum(d[[colname]] == as.integer(d[[colname]]),na.rm = TRUE) == 0
        ) {
      # Numerical variable. Histogram with Rice's Rule

      # If there are NA's, stratify on those

      na_count = sum(is.na(tmp[[colname]]))
      not_na_count = length(tmp[[colname]]) - na_count

      s = sample(c(0,1),prob = c(not_na_count,na_count),1)

      if (s == 0) {
        # Histogram stratification based on breaks calculated on the
        # population

        n_breaks = floor(2*sum(!is.na(d[[colname]]))**((1/3)))
        bar_size = (max(d[[colname]],na.rm = TRUE)-min(d[[colname]],na.rm = TRUE))/n_breaks

        breaks = sapply(0:n_breaks,function(i) {min(d[[colname]],na.rm = TRUE) + i*bar_size})

        h = hist(tmp[[colname]],breaks=breaks,plot = F)

        # Select one bar of the histogram according to the density
        bar_id  = sample(1:length(h$mids),prob = h$counts,1)

        bar_start = h$breaks[bar_id]
        bar_end = h$breaks[bar_id + 1]

        tmp = tmp[tmp[[colname]] >= bar_start & tmp[[colname]] < bar_end & !is.na(tmp[[colname]]),]
      } else {
        # NA
        tmp = tmp[is.na(tmp[[colname]]),]
      }

    } else {
      # Categorical variable

      # Histogram for the selected dimension
      aggr = as.data.frame(table(tmp[,colname],useNA="ifany"))
      names(aggr) = c("dim","count")

      # Generate a value according to the histogram
      generated_value = sample(aggr$dim,prob=aggr$count,1)

      # Slice the actual multivariate histogram in order to
      # take only records with the selected value on the
      # selected dimension
      if (!is.na(generated_value)) {
        tmp = tmp[tmp[[colname]] == generated_value & !is.na(tmp[[colname]]),]
      }
      else {
        tmp = tmp[is.na(tmp[[colname]]),]
      }

    }

  }

  # Once the procedure finishes, we get a bulk of records
  # with the same values of each dimension. Let's take
  # one of these records uniformly
  random_index = sample(1:nrow(tmp),1)
  new_record = tmp[random_index,]

  # Let's remove duplicates
  inserted_record = sqldf("select * from new_record except select * from generated2")

  # Insert in the "train" data frame and repeat until desired sample size is reached
  generated2 = unique(rbind(generated2,inserted_record))
}
```

**Manual adjustment**

```{r adjust}
# Work with a temporary table for manual adjustments
split1 <- trainkids %>% 
  mutate(which.dataset = ifelse(
    childID %in% generated2$childID, "1_validate", "1_train"
  ))
table(split1$which.dataset)

## VIEW
# select(split1, childID,
#                            child.gender,
#                            child.age.bin,
#                            parent.race.nonwhite,
#                            which.dataset) %>%
#   arrange(child.age.bin, child.gender, parent.race.nonwhite, which.dataset) %>%
#   view()

## MANUAL ADJUSTMENT
split1$which.dataset[split1$childID %in% 
                       c("09c87d6e-36c0-455d-812d-4576b1b0eefd" #7 M W
                         ,"196cf907-a938-441a-8734-92e5ae5e1890" #7m M W
                         )
                           ] <- "1_train"

split1$which.dataset[split1$childID %in% 
                           c(
                             "WIH7v" #4m F NW
                             ,"4e3e2517-4788-45ae-94cb-1a0dbd22d4d7"
                             ,"3ae67b03-bb6b-4c98-a6e3-55581f4b322b" #7 F NW
                             ,"4e3e2517-4788-45ae-94cb-1a0dbd22d4d7" #10 M NW
                             ,"c409b6f6-6cce-46e2-b1ac-47299ba53a83" #7 F NW
                           )] <- "1_validate"

table(split1$which.dataset)

# Plot
with(split1, table(which.dataset, child.age.bin, parent.race.nonwhite, child.gender))

# Update participants table
validatekids <- split1  %>% 
  filter(which.dataset=="1_validate")

participants_ML[participants_ML$childID %in% validatekids$childID, 'which.dataset'] <- "1_validate"
```

## Manual adjustment

2022-04-10: Maximize the number of doubly-coded children in test 

```{r}
participants_ML$which.dataset[participants_ML$childID %in% 
                       c("4255d6cf-4135-4e44-bece-1ac29297661b",	#10,m,w
                         "Wve6h", #10,m,w
                         "7ecbcfe7-2ac3-4a47-8b7d-8c79da576a28",#4,f,w
                         "763768d1-6f04-4ebe-a722-5d1167708ac7",#7,f,nw
                         "MTBMm" #7m,f,w
                         )
                           ] <- "1_train"

participants_ML$which.dataset[participants_ML$childID %in% 
                           c("H1Ree",#	10m,f,w
                             "PMdsp",#	10m,m,nw
                             "1bda1d34-93e1-4609-b0a2-c26c5c01f167"#	7m,f,w
                           )] <- "1_validate"

participants_ML$which.dataset[participants_ML$childID %in% 
                       c("43fe8a51-0325-4362-9c5f-b343fb1f6cda", #10 F NW
                         "4e3e2517-4788-45ae-94cb-1a0dbd22d4d7", #10 F NW
                         "193222a9-1e75-4729-812c-01f757858b76", #10 M W
                         "1cb796b7-debc-49b9-bba1-d107a33ea4a3", #10 M W
                         "340f7b69-4125-42dc-b632-49a57f379c8a", #4 F W
                         "501b9e5b-b070-4cbb-9dc2-395cfad9b421", #7 F NW
                         "c409b6f6-6cce-46e2-b1ac-47299ba53a83", #7 F W
                         "acb7722c-7eb3-4936-abca-23d0860532b9" #7 F W
                         )
                           ] <- "2_test"
```


# Report splits

### Mosaic Plot

```{r mosaic_div}
# plot
ggplot(participants_ML) +
  geom_mosaic(aes(x=product(child.age.bin, parent.race.nonwhite),
                  fill=child.gender,
              alpha=parent.race.nonwhite))+
  facet_wrap(.~which.dataset, drop = T)+
  scale_alpha_manual(values =c(.9,.6)) +
  labs(x="Gender : Race", y="Age")+
    theme_mosaic()+
  theme(axis.text.x = element_text(angle = 90))
```
### Race

```{r}
# Plot
ggplot(participants_ML) +
  geom_mosaic(aes(x=product(which.dataset), fill=parent.race.nonwhite))

# Counts
with(participants_ML, table(parent.race.nonwhite, which.dataset))
# Proportions
with(participants_ML, table(parent.race.nonwhite, which.dataset))%>% 
  prop.table(margin=2)
```

### Age
```{r}
# Plot
ggplot(participants_ML) +
  geom_mosaic(aes(x=product(which.dataset), fill=child.age.bin))
#Counts
with(participants_ML, table(child.age.bin, which.dataset))
# Proportions
with(participants_ML, table(child.age.bin, which.dataset))%>% 
  prop.table(margin=2)
```


### Sex
```{r}
# Plot
ggplot(participants_ML) +
  geom_mosaic(aes(x=product(which.dataset), fill=child.gender))
# Counts
with(participants_ML, table(child.gender, which.dataset))
# Proportions
with(participants_ML, table(child.gender, which.dataset)) %>% 
  prop.table(margin=2)
```


### Race X gender
```{r}
# Proportions
with(participants_ML, table(parent.race.nonwhite, child.gender, which.dataset))%>% 
  prop.table(margin='which.dataset') %>%
  addmargins(margin=c(1,2))
# Plot
ggplot(participants_ML) +
  geom_mosaic(aes(x=product(parent.race.nonwhite, which.dataset),
                  fill=child.gender, alpha=parent.race.nonwhite)) +
  scale_alpha_manual(values=c(.9, .6)) +
      theme_mosaic()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

### Age X gender

```{r}
with(participants_ML, table(child.age.bin, child.gender, which.dataset))%>% 
  prop.table(margin='which.dataset') %>%
  addmargins(margin=c(1,2))
# Plot
ggplot(participants_ML) +
  geom_mosaic(aes(x=product(which.dataset, child.age.bin),
                  fill=child.gender,alpha=which.dataset))+
  scale_alpha_manual(values =c(.9,.3, .6))+
      theme_mosaic()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

### Age X race
```{r}
with(participants_ML, table(child.age.bin, parent.race.nonwhite, which.dataset))%>% 
  prop.table(margin='which.dataset') %>%
  addmargins(margin=c(1,2))
# Plot
ggplot(participants_ML) +
  geom_mosaic(aes(x=product(child.age.bin,parent.race.nonwhite),
                  alpha=parent.race.nonwhite, fill=child.age.bin))+
  facet_wrap(.~which.dataset)+
  scale_alpha_manual(values =c(.9,.6))+
      theme_mosaic()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

# Move Files

```{r}
df.annotations<- read_tsv(paste0(lookitdir, "annotations.tsv")) %>%
  select(videoID, codingFile1:codingFile3)
videos <- left_join(videos, df.annotations, by="videoID")

```

<!-- Read in list of annotation files -->

<!-- ```{r} -->
<!-- df.annotations<- read_csv(paste0(lookitdir, "Annotation-list-all.csv")) %>% -->
<!--   filter(videoID %in% df.videos$videoID) -->
<!-- # check counts -->
<!-- nrow(df.annotations %>% distinct(videoID)) -->
<!-- ``` -->

<!-- Add annotation file names to video list -->

<!-- ```{r} -->
<!-- videos <- left_join(videos, df.annotations, -->
<!--                        by=c(studyID="studyID", childID="childID", videoID='videoID', coder1='coderID')) %>% -->
<!--   rename(codingFile1=annotationFileName) -->
<!-- #add coder 2 -->
<!-- videos <- left_join(videos, df.annotations,  -->
<!--                        by=c(studyID="studyID", childID="childID", videoID='videoID', coder2='coderID')) %>% -->
<!--   rename(codingFile2=annotationFileName) -->

<!-- # now add coder 3 -->
<!-- videos<- left_join(videos, df.annotations,  -->
<!--                        by=c(studyID="studyID", childID="childID", videoID='videoID', coder3='coderID')) %>% -->
<!--   rename(codingFile3=annotationFileName) -->

<!-- ``` -->

## Export file list

```{r}
filelist<-df.videos %>% filter(privacy != "private") %>%
  filter(!is.na(coder1)) 

filelist %>%
  write_csv(paste0(qidir, "filelist.csv"))
```

## Copy Videos

<!-- ```{r include=FALSE} -->
<!-- file.copy(from=paste0(lookitdir,"video/", filelist$videoFileName), -->
<!--           to= qidir, -->
<!--           copy.date=T, overwrite = F) # don't overwrite -->

<!-- # move all the coded ones to separate folder -->
<!-- #file_move(paste0(qidir, df.videos$videoFileName[!is.na(df.videos$coder1)]), -->
<!-- #          paste0(qidir, "annotated/")) -->
<!-- ``` -->

<!-- Check videos are indeed in the folder -->

<!-- ```{r echo=TRUE} -->
<!-- summary(file.exists(paste0(qidir, 'videos/', filelist$videoFileName))) -->

<!-- # get missing files -->
<!-- # (missing<- setdiff(list.files(paste0(qidir, 'videos/')), -->
<!-- #                  filelist$videoFileName)) -->
<!-- ``` -->


<!-- ## Copy Annotations -->

<!-- ```{r include=FALSE} -->
<!-- # coder 1 -->
<!-- file.copy(from=paste0(lookitdir, "annotations originalname/", -->
<!--                       na.omit(videos$codingFile1)), -->
<!--           to= paste0(qidir, "annotations/coder1/", na.omit(videos$codingFile1)), -->
<!--           copy.date=T, overwrite = F) # don't overwrite -->

<!-- # coder 2 -->
<!-- file.copy(from=paste0(lookitdir, "annotations/", -->
<!--                       na.omit(videos$codingFile2)), -->
<!--           to= paste0(qidir, "annotations/coder2/", -->
<!--                      na.omit(videos$codingFile2)), -->
<!--           copy.date=T, overwrite = F) # don't overwrite -->

<!-- # coder 3 -->
<!-- file.copy(from=paste0(lookitdir, "annotations/", -->
<!--                       na.omit(videos$codingFile3)), -->
<!--           to= paste0(qidir, "annotations/coder3/", -->
<!--                      na.omit(videos$codingFile3)), -->
<!--           copy.date=T, overwrite = F) # don't overwrite -->
<!-- ``` -->

<!-- Check -->

<!-- ```{r} -->
<!-- #check -->
<!-- summary(file.exists(paste0(qidir, "annotations/coder1/", -->
<!--                        na.omit(videos$codingFile1)))) -->

<!-- #check -->
<!-- summary(file.exists(paste0(qidir, "annotations/coder2/", -->
<!--                        na.omit(videos$codingFile2)))) -->

<!-- #check -->
<!-- summary(file.exists(paste0(qidir, "annotations/coder3/", -->
<!--                        na.omit(videos$codingFile3)))) -->

<!-- ``` -->


# Export split as tsv

```{r}
#rename(participants_ML, studyID = studyid)

write_tsv(participants_ML, paste0(lookitdir,"VideosForQI/prefphys_split0_participants.tsv"))
write_tsv(participants_ML, paste0(qidir, "prephys_split0_participants.tsv"))

#
thelist<- videos %>% 
  left_join(select(participants_ML, studyid, childID, which.dataset),
                     by=c(studyID="studyid",childID="childID")) %>%
  filter(!is.na(which.dataset),
         !is.na(codingFile1)) %>% 
  select(studyID, childID, videoID, n_coders, videoFileName, 
         codingFile1:codingFile3,
         child.ageSessionRounded, child.gender, parent.race.nonwhite,
         video.privacy, consentnotes:video.actualDuration, which.dataset) 

write_tsv(thelist, paste0(lookitdir, "VideosForQI/prephys_split0_videos.tsv"))
write_tsv(thelist, paste0(qidir, "prephys_split0_videos.tsv"))
```

