---
title: "01_Generate-Split"
author: "Junyi Chu"
date: '2022-01-12'
output:
  html_document:
    df_print: paged
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

# Setup 

Do some basic R setup, import packages, set random seed.

```{r setup, include=F}
# clear memory and run garbage collector
rm(list = ls()); gc()
# Load packages
if(!require("pacman")) install.packages("pacman")
pacman::p_load('tidyverse', 'stringr', 'rstudioapi', 'knitr')
# set default chunk options 
knitr::opts_chunk$set(
	fig.height = 4,
	fig.width = 6,
	message = FALSE,
	warning = FALSE
)
# Random seed
set.seed(12341)
```



```{r import, include=F}
# List of video files available for scientific use
df.sessions.raw <- read_csv("~/Downloads/march/Cal_BW_March_split0_videos.csv", 
                                   col_types = cols(n_coders = col_integer(), 
                                                    uniqueID = col_integer())) %>%
    mutate(race.nonwhite = if_else(race.ethnic == "White", "White", "NonWhite"),
         age = as.factor(floor((child.ageSessionRounded +1)/ 4)*4 -1),
         preterm = ifelse(is.na(study.notes), FALSE, 
                          ifelse(study.notes=="preterm", TRUE, FALSE)))
```

### Check dataset

```{r}
length(unique(df.sessions.raw$childID)) #216 unique children
```

## Participant Table

We want the variables:

- age at session 1 (in months)
- gender (m/f)
- race (nonwhite yes, no, or NA)
- number of sessions / videos available
- number of videos coded
- country

```{r}
participants <- df.sessions.raw %>% filter(uniqueID == 1) %>%
  select(videoFileName, 
         childID, 
         race.ethnic, child.ageSessionRounded, child.gender, study.notes,
         race.nonwhite, age, preterm)
```



```{r}
df.sessions.raw %>% # plot
  ggplot(aes(x=reorder(childID, child.ageSessionRounded))) +
  geom_point(aes(y=child.ageSessionRounded), alpha=0.5) +
  labs(y='Age (months)', x='Child', title='Data availability by age and race') +
  facet_grid(vars(race.nonwhite)) +
  theme(axis.text.x=element_text(size = 5))
```

## Age

We have some variability by age. The coded set reflects this distribution:

```{r}
participants %>%
  ggplot() +
  geom_bar(aes(x=age),
           color='black') +
  labs(title="Unique kids by age",
       x="Age") +
  theme_bw()+
  theme(legend.position = c(.75, .95),
    legend.justification = c("left", "top"))
```

Since each child contributes multiple sessions,we can look at overall dataset by session:

```{r}
df.sessions.raw %>%
  ggplot() +
  geom_bar(aes(x=child.ageSessionRounded),
           color='black')+
  labs(title="Sessions by age", 
       x="Age (months)") +
  theme_bw()+
  theme(legend.position = c(.75, .95),
    legend.justification = c("left", "top"))
```

## Gender

We have an even mix of gender (male/female), but we could code more females.

```{r}
ggplot(participants, aes(x=child.gender)) +
  geom_bar(aes(x=child.gender),
           color='black') +
  labs(title="Unique kids by gender",
       x="Gender (female/male)") +
  theme_bw()+
  theme(legend.position = c(.75, .95),
    legend.justification = c("left", "top"))
```

## Race

Participants by race and coding status. There are 12 non-white participants we can code.

```{r}
df.sessions.raw %>% filter(uniqueID==1) %>%
ggplot(aes(x=race.ethnic)) +
  geom_bar()

## binary
ggplot(participants, aes(x=race.nonwhite)) +
  geom_bar()
```

# Sampling procedure

### Mosaic plot 

Graph race, sex and age -- we want to split this into even sets.

```{r mosaic_all, include=TRUE}
library(ggmosaic)
ggplot(data = participants) +
  #geom_mosaic(aes(x=product(age, race.nonwhite),
  #                fill=child.gender)) + 
  geom_mosaic(aes(x=product(age, race.nonwhite),
                  fill=child.gender,
              alpha=race.nonwhite))+
  scale_alpha_manual(values =c(.9,.6)) +
  labs(x="Gender : Race", y="Age")+
    theme_mosaic()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

### Race

```{r, include=TRUE}
participants %>% 
  count(race.nonwhite) %>%
  mutate(prop = n/sum(n),
         target_n = n*.7)
```

### Age

Note that repeat sessions will be older in age, but still within 2 months of first session. 

```{r, include=T}
participants %>% 
  count(age) %>%
  mutate(prop = n/sum(n),
         target_n = n*.7)
```


### Sex

```{r, include=T}
participants %>% 
  count(child.gender) %>%
  mutate(prop = n/sum(n),
         target_n = n*.7)
```

## Generate split

We follow procedure in [https://towardsdatascience.com/stratified-sampling-and-how-to-perform-it-in-r-8b753efde1ef](https://towardsdatascience.com/stratified-sampling-and-how-to-perform-it-in-r-8b753efde1ef)

```{r}
n_training_kids = round(.7*nrow(participants))
n_test_kids = nrow(participants) - n_training_kids
n_validation_kids = round(.2*n_training_kids)
```

We're targeting 30% for test (n= `r n_test_kids` kids) and 70% for training (n= `r n_training_kids`). Training set will be further divided into 20% for validation (`r n_validation_kids`). 

### First split into 70/30 train/test

```{r include=FALSE}
# Set seed
set.seed(123)
# Make simplified dataset to sample from
d = participants
n_sample = n_training_kids
generated = head(d,0)
dimensions = c("age", "race.nonwhite", "child.gender", "preterm")
library(sqldf)
while (nrow(generated) < n_sample) {
  # For debug purposes
  cat(nrow(generated),"\n")
  flush.console()

  tmp = d

  # Calculate the histogram for each dimension
  # and select one value at a time, slicing the
  # original dataset according to its histogram
  for (i in 1:length(dimensions)) {

    colname = dimensions[i]
    if (class(d[[colname]]) %in% c("numeric") &&
        sum(d[[colname]] == as.integer(d[[colname]]),na.rm = TRUE) == 0
        ) {
      # Numerical variable. Histogram with Rice's Rule

      # If there are NA's, stratify on those

      na_count = sum(is.na(tmp[[colname]]))
      not_na_count = length(tmp[[colname]]) - na_count

      s = sample(c(0,1),prob = c(not_na_count,na_count),1)

      if (s == 0) {
        # Histogram stratification based on breaks calculated on the
        # population

        n_breaks = floor(2*sum(!is.na(d[[colname]]))**((1/3)))
        bar_size = (max(d[[colname]],na.rm = TRUE)-min(d[[colname]],na.rm = TRUE))/n_breaks

        breaks = sapply(0:n_breaks,function(i) {min(d[[colname]],na.rm = TRUE) + i*bar_size})

        h = hist(tmp[[colname]],breaks=breaks,plot = F)

        # Select one bar of the histogram according to the density
        bar_id  = sample(1:length(h$mids),prob = h$counts,1)

        bar_start = h$breaks[bar_id]
        bar_end = h$breaks[bar_id + 1]

        tmp = tmp[tmp[[colname]] >= bar_start & tmp[[colname]] < bar_end & !is.na(tmp[[colname]]),]
      } else {
        # NA
        tmp = tmp[is.na(tmp[[colname]]),]
      }

    } else {
      # Categorical variable

      # Histogram for the selected dimension
      aggr = as.data.frame(table(tmp[,colname],useNA="ifany"))
      names(aggr) = c("dim","count")

      # Generate a value according to the histogram
      generated_value = sample(aggr$dim,prob=aggr$count,1)

      # Slice the actual multivariate histogram in order to
      # take only records with the selected value on the
      # selected dimension
      if (!is.na(generated_value)) {
        tmp = tmp[tmp[[colname]] == generated_value & !is.na(tmp[[colname]]),]
      }
      else {
        tmp = tmp[is.na(tmp[[colname]]),]
      }

    }

  }

  # Once the procedure finishes, we get a bulk of records
  # with the same values of each dimension. Let's take
  # one of these records uniformly
  random_index = sample(1:nrow(tmp),1)
  new_record = tmp[random_index,]

  # Let's remove duplicates
  inserted_record = sqldf("select * from new_record except select * from generated")

  # Insert in the "train" data frame and repeat until desired sample size is reached
  generated = unique(rbind(generated,inserted_record))
}

# Save as a variable in the participants list
participants <- participants %>% 
  mutate(which.dataset = ifelse(
    childID %in% na.omit(generated$childID),
    "1_train","2_test"))
rm(tmp)
```

**Manual adjustment**

```{r}
# Work with a temporary table for manual adjustments
split0 <- participants
table(split0$which.dataset)

## VIEW
select(split0, childID,
       child.gender,
       age,
       race.nonwhite,
       preterm,
       which.dataset) %>%
  arrange(age, child.gender, race.nonwhite, preterm, which.dataset) %>%
  view()
```

### check and adjust

```{r}
## MANUAL ADJUSTMENT
# TRAIN: +15, +19, +23
split0$which.dataset[split0$childID %in% 
                           c("7606", "8644", "11742", "7605", "12840", "7519",
                             "6688", "11958", "12683", "11754", "5802", "6230",
                             "11766", "6313", "4128", "8588")] <- "1_train"

split0$which.dataset[split0$childID %in% 
                           c("6313", "11766", "11807", "11881", "12220", "11005",
                              "8643", "13204", "13142", "20123",
                             "11591", "11339", 
                             "6575", "13331", "13406")] <- "2_test"

# Mosaic plot
ggplot(split0) +
  geom_mosaic(aes(x=product(age, child.gender),
                  fill=which.dataset,
              alpha=which.dataset))+
  facet_wrap(.~race.nonwhite, drop = T)+
  scale_alpha_manual(values =c(.9,.6)) +
#  labs(x="Gender : which.dataset", y="Age")+
    theme_mosaic()+
  theme(axis.text.x = element_text(angle = 90))

# RACE
ggplot(split0) +
  geom_mosaic(aes(x=product(which.dataset), fill=race.nonwhite))

with(split0, table(race.nonwhite, which.dataset))

with(split0, table(race.nonwhite, which.dataset))%>% 
  prop.table(margin=1)

# AGE
ggplot(split0) +
  geom_mosaic(aes(x=product(which.dataset), fill=age))

with(split0, table(age, which.dataset))

with(split0, table(age, which.dataset))%>% 
  prop.table(margin=1)

## SEX
ggplot(split0) +
  geom_mosaic(aes(x=product(which.dataset), fill=child.gender))

with(split0, table(child.gender, which.dataset))

with(split0, table(child.gender, which.dataset)) %>% 
  prop.table(margin=1)

# preterm

ggplot(split0) +
  geom_mosaic(aes(x=product(which.dataset), fill=preterm))

with(split0, table(preterm, which.dataset))

with(split0, table(preterm, which.dataset)) %>% 
  prop.table(margin=1)
```


### commit!

```{r}
participants<- split0
testkids <- participants %>% 
  filter(which.dataset=="2_test")
trainkids <- participants %>% 
  filter(which.dataset=="1_train")
```



### Split train into train/validate


80/20


```{r sample, include=FALSE}
# Set seed
set.seed(1241)
# Sample from training set
d = trainkids
generated2 = head(d,0)
dimensions = c("age", "race.nonwhite", "child.gender", "preterm")
while (nrow(generated2) < n_validation_kids) {
  # For debug purposes
  cat(nrow(generated2),"\n")
  flush.console()

  tmp = d

  # Calculate the histogram for each dimension
  # and select one value at a time, slicing the
  # original dataset according to its histogram
  for (i in 1:length(dimensions)) {

    colname = dimensions[i]
    if (class(d[[colname]]) %in% c("numeric") &&
        sum(d[[colname]] == as.integer(d[[colname]]),na.rm = TRUE) == 0
        ) {
      # Numerical variable. Histogram with Rice's Rule

      # If there are NA's, stratify on those

      na_count = sum(is.na(tmp[[colname]]))
      not_na_count = length(tmp[[colname]]) - na_count

      s = sample(c(0,1),prob = c(not_na_count,na_count),1)

      if (s == 0) {
        # Histogram stratification based on breaks calculated on the
        # population

        n_breaks = floor(2*sum(!is.na(d[[colname]]))**((1/3)))
        bar_size = (max(d[[colname]],na.rm = TRUE)-min(d[[colname]],na.rm = TRUE))/n_breaks

        breaks = sapply(0:n_breaks,function(i) {min(d[[colname]],na.rm = TRUE) + i*bar_size})

        h = hist(tmp[[colname]],breaks=breaks,plot = F)

        # Select one bar of the histogram according to the density
        bar_id  = sample(1:length(h$mids),prob = h$counts,1)

        bar_start = h$breaks[bar_id]
        bar_end = h$breaks[bar_id + 1]

        tmp = tmp[tmp[[colname]] >= bar_start & tmp[[colname]] < bar_end & !is.na(tmp[[colname]]),]
      } else {
        # NA
        tmp = tmp[is.na(tmp[[colname]]),]
      }

    } else {
      # Categorical variable

      # Histogram for the selected dimension
      aggr = as.data.frame(table(tmp[,colname],useNA="ifany"))
      names(aggr) = c("dim","count")

      # Generate a value according to the histogram
      generated_value = sample(aggr$dim,prob=aggr$count,1)

      # Slice the actual multivariate histogram in order to
      # take only records with the selected value on the
      # selected dimension
      if (!is.na(generated_value)) {
        tmp = tmp[tmp[[colname]] == generated_value & !is.na(tmp[[colname]]),]
      }
      else {
        tmp = tmp[is.na(tmp[[colname]]),]
      }

    }

  }

  # Once the procedure finishes, we get a bulk of records
  # with the same values of each dimension. Let's take
  # one of these records uniformly
  random_index = sample(1:nrow(tmp),1)
  new_record = tmp[random_index,]

  # Let's remove duplicates
  inserted_record = sqldf("select * from new_record except select * from generated2")

  # Insert in the "train" data frame and repeat until desired sample size is reached
  generated2 = unique(rbind(generated2,inserted_record))
}
```

**Manual adjustment**

```{r adjust}
# Work with a temporary table for manual adjustments
split1 <- trainkids %>% 
  mutate(which.dataset = ifelse(
    childID %in% generated2$childID, "1_validate", "1_train"
  ))
table(split1$which.dataset)

```


check and adjust

```{r}

## MANUAL ADJUSTMENT
split1$which.dataset[split1$childID %in% 
                       c("5623", "12612"
                         )] <- "1_train"

split1$which.dataset[split1$childID %in% 
                           c("7773", "11037", "12840")] <- "1_validate"

table(split1$which.dataset)

## VIEW
select(split1, childID,
                           child.gender,
                           age,
                           race.nonwhite, preterm,
                           which.dataset) %>%
  arrange(age, child.gender, race.nonwhite, preterm, which.dataset) %>%
  view()

# RACE
ggplot(split1) +
  geom_mosaic(aes(x=product(which.dataset), fill=race.nonwhite))

with(split1, table(race.nonwhite, which.dataset))

with(split1, table(race.nonwhite, which.dataset))%>% 
  prop.table(margin=1)

# AGE
ggplot(split1) +
  geom_mosaic(aes(x=product(which.dataset), fill=age))

with(split1, table(age, which.dataset))

with(split1, table(age, which.dataset))%>% 
  prop.table(margin=1)

## SEX
ggplot(split1) +
  geom_mosaic(aes(x=product(which.dataset), fill=child.gender))

with(split1, table(child.gender, which.dataset))

with(split1, table(child.gender, which.dataset)) %>% 
  prop.table(margin=1)

# preterm

ggplot(split1) +
  geom_mosaic(aes(x=product(which.dataset), fill=preterm))

with(split1, table(preterm, which.dataset))

with(split1, table(preterm, which.dataset)) %>% 
  prop.table(margin=1)

# Update participants table
validatekids <- split1  %>% 
  filter(which.dataset=="1_validate")

participants[participants$childID %in% validatekids$childID, 'which.dataset'] <- "1_validate"

```

Final check

```{r}

participants$which.dataset[participants$childID %in% 
                       c("6282")] <- "1_validate"
participants$which.dataset[participants$childID %in% 
                       c("5957")] <- "1_train"

```

# Report splits

### Mosaic Plot

```{r mosaic_div}
# plot
ggplot(participants) +
  geom_mosaic(aes(x=product(age, race.nonwhite),
                  fill=child.gender,
              alpha=race.nonwhite))+
  facet_wrap(.~which.dataset, drop = T)+
  scale_alpha_manual(values =c(.9,.6)) +
  labs(x="Gender : Race", y="Age")+
    theme_mosaic()+
  theme(axis.text.x = element_text(angle = 90))
```
### Race

```{r}
# Plot
ggplot(participants) +
  geom_mosaic(aes(x=product(which.dataset), fill=race.nonwhite))

# Counts
with(participants, table(race.nonwhite, which.dataset))
# Proportions
with(participants, table(race.nonwhite, which.dataset))%>% 
  prop.table(margin=2)
```

### Age
```{r}
# Plot
ggplot(participants) +
  geom_mosaic(aes(x=product(which.dataset), fill=age))
#Counts
with(participants, table(age, which.dataset))
# Proportions
with(participants, table(age, which.dataset))%>% 
  prop.table(margin=2)
```


### Sex
```{r}
# Plot
ggplot(participants) +
  geom_mosaic(aes(x=product(which.dataset), fill=child.gender))
# Counts
with(participants, table(child.gender, which.dataset))
# Proportions
with(participants, table(child.gender, which.dataset)) %>% 
  prop.table(margin=2)
```

### Preterm
```{r}
# Plot
ggplot(participants) +
  geom_mosaic(aes(x=product(which.dataset), fill=preterm))

```

### Race X gender
```{r}
# Proportions
with(participants, table(race.nonwhite, child.gender, which.dataset))%>% 
  prop.table(margin='which.dataset') %>%
  addmargins(margin=c(1,2))
# Plot
ggplot(participants) +
  geom_mosaic(aes(x=product(race.nonwhite, which.dataset),
                  fill=child.gender, alpha=race.nonwhite)) +
  scale_alpha_manual(values=c(.9, .6)) +
      theme_mosaic()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

### Age X gender

```{r}
with(participants, table(age, child.gender, which.dataset))%>% 
  prop.table(margin='which.dataset') %>%
  addmargins(margin=c(1,2))
# Plot
ggplot(participants) +
  geom_mosaic(aes(x=product(which.dataset, age),
                  fill=child.gender,alpha=which.dataset))+
  scale_alpha_manual(values =c(.9,.3, .6))+
      theme_mosaic()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

### Age X Preterm

```{r}
# Plot
ggplot(participants) +
  geom_mosaic(aes(x=product(which.dataset, age),
                  fill=preterm,alpha=which.dataset))+
  scale_alpha_manual(values =c(.9,.3, .6))+
      theme_mosaic()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

### Age X race
```{r}
with(participants, table(age, race.nonwhite, which.dataset))%>% 
  prop.table(margin='which.dataset') %>%
  addmargins(margin=c(1,2))
# Plot
ggplot(participants) +
  geom_mosaic(aes(x=product(age,race.nonwhite),
                  alpha=which.dataset, fill=age))+
  scale_alpha_manual(values =c(.9,.3, .6))+
  facet_wrap(.~race.nonwhite)+
#  scale_alpha_manual(values =c(.9,.6))+
      theme_mosaic()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

### Preterm X gender
```{r}
with(participants, table(child.gender, preterm, which.dataset))%>% 
  prop.table(margin='which.dataset') %>%
  addmargins(margin=c(1,2))
# Plot
ggplot(participants) +
  geom_mosaic(aes(x=product(child.gender,preterm),
                  alpha=which.dataset, fill=preterm))+
  scale_alpha_manual(values =c(.9,.3, .6))+
      theme_mosaic()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```


# Export split as tsv

```{r}
participants <- participants %>%
  left_join(select(df.sessions.raw, videoFileName,
                   reliabilityFileName, originalFileName,
                   timestamp.vidstart, studyID, study.order, vid.color, privacy, n_coders),
            by="videoFileName") %>%
  relocate(c('videoFileName', 'reliabilityFileName', 'originalFileName')) %>%
participants <- participants %>%
  rename(codingFile1=reliabilityFileName,
         codingFile2=originalFileName)

participants %>% 
  write_csv("Cal_BW_March_split0_participants.csv")
table(participants$which.dataset)
```

# HASHIDS

We want original session/child uuids, one set for videos, one set for demographics, and the key linking all three

```{r}
library(digest)
hashkey <- select(participants, studyID, childID)
hashkey$childID.video <- sapply(hashkey$childID, digest, algo = "murmur32", seed="111")
hashkey$childID.demographics <- sapply(hashkey$childID, digest, algo = "murmur32", seed="222")
# check for duplicates across hashes
sum(hashkey$childID.video==hashkey$childID.demographics)
# Check for duplicates in the allraw dataset
hashkey %>% distinct(childID) %>% dim 
hashkey %>% distinct(childID.demographics) %>% dim # 216 unique kids
hashkey %>% distinct(childID.video) %>% dim # 216 unique kids,1 video per kid

# save the key ----
write_csv(hashkey, "Cal_BW_March_split0_hashids.csv")

# save the participant list with hashed IDS
participants.hashed <- participants %>%
  left_join(hashkey, by=c('childID', 'studyID')) %>%
  select(-childID) %>%
  mutate(videoFileName.hashed = paste0("study-CalBW", 
                                       "_child-", childID.demographics, 
                                       "_video-", childID.video, ".mov"),
         codingFile1.hashed = paste0("study-CalBW", 
                                       "_child-", childID.demographics, 
                                       "_video-", childID.video, 
                                       "_coding1.vcx"),
         codingFile2.hashed = paste0("study-CalBW", 
                                       "_child-", childID.demographics, 
                                       "_video-", childID.video, 
                                       "_coding2.vcx")) %>%
  select(videoFileName.hashed, codingFile1.hashed, codingFile2.hashed,
         which.dataset,
         child.gender, race.nonwhite, age, preterm, 
         n_coders, vid.color, timestamp.vidstart)
write_csv(participants.hashed, "Cal_BW_March_split0_participants_hashed.csv")

```
