---
title: "02_Move-files-for-QI"
author: "Junyi Chu"
date: '2022-01-12'
output:
  html_document:
    df_print: paged
    code_folding: hide
---

This notebook takes in a train/test split list of videos and copies video files into the PrefPhys dropbox folder for QI

# Setup 

Do some basic R setup, import packages, set random seed.
```{r}
rm(list = ls())
if(!require("pacman")) install.packages("pacman")
pacman::p_load('tidyverse', 'fs', 'stringr', 'knitr')
knitr::opts_chunk$set(
  warning = TRUE, # show warnings during codebook generation
  message = TRUE, # show messages during codebook generation
  error = TRUE # do not interrupt codebook generation in case of errors,
                # TRUE is usually better for debugging
)
ggplot2::theme_set(ggplot2::theme_bw())
# Random seed
set.seed(12341)

lookitdir <- "/Volumes/LookitVideo/PrefPhys-coding/"
qidir <- "/Users/junyichu/Dropbox (MIT)/2 NOW/2018 Physics/Videos for QI/"
```

This notebook takes as input a list of sessions which also contains some demographic variables. For now, we use original session uuids, lookit user ids, etc. Eventually we want to use deidentified IDs.

Read in video list

```{r}
# List of video files available for scientific use (both coded and not yet)
df.videos<- read_csv(paste0(lookitdir, "ForQI/prefphys_split0_videos.tsv"))
```

Read in annotation list 

```{r}
df.annotations<- read_csv(paste0(lookitdir, "Annotation-list-all.csv")) %>%
  filter(videoID %in% df.videos$videoID)
# check counts
nrow(df.annotations %>% distinct(videoID))
```

Add annotation file names to video list

```{r}
df.videos <- left_join(df.videos, df.annotations,
                       by=c(studyID="studyID", childID="childID", videoID='videoID', coder1='coderID')) %>%
  rename(codingFile1=annotationFileName) %>%
  # now add coder 2
  left_join(df.annotations, 
                       by=c(studyID="studyID", childID="childID", videoID='videoID', coder2='coderID')) %>%
  rename(codingFile2=annotationFileName) %>%
  # now add coder 3
  left_join(df.annotations, 
                       by=c(studyID="studyID", childID="childID", videoID='videoID', coder3='coderID')) %>%
  rename(codingFile3=annotationFileName)

```

# Copy Videos


Now copy

```{r eval=FALSE}
file.copy(from=paste0(qidir,"video/", df.videos$videoFileName),
          to= qidir,
          copy.date=T, overwrite = F) # don't overwrite

# move all the coded ones to separate folder
#file_move(paste0(qidir, df.videos$videoFileName[!is.na(df.videos$coder1)]),
#          paste0(qidir, "annotated/"))
```

Check videos are indeed in the folder

```{r echo=TRUE}
# ok all 365 are there
sum(file.exists(paste0(qidir, 'videos/', df.videos$videoFileName)))

```


# Copy Annotations

```{r eval=FALSE}
file.copy(from=paste0(qidir, "annotations/", na.omit(df.videos$codingFile1)),
          to= paste0("/Users/junyichu/Dropbox (MIT)/2 NOW/2018 Physics/Videos for QI/annotations/coder1/", na.omit(df.videos$codingFile1)),
          copy.date=T, overwrite = F) # don't overwrite

# coder 2
file.copy(from=paste0(qidir, "annotations/", na.omit(df.videos$codingFile2)),
          to= paste0(qidir, "annotations/coder2/", na.omit(df.videos$codingFile2)),
          copy.date=T, overwrite = F) # don't overwrite

# coder 3
file.copy(from=paste0(qidir, "annotations/", na.omit(df.videos$codingFile3)),
          to= paste0(qidir, "annotations/coder3/", na.omit(df.videos$codingFile3)),
          copy.date=T, overwrite = F) # don't overwrite
```

Check

```{r}
#check
sum(file.exists(paste0(qidir, "annotations/coder1/",
                       na.omit(df.videos$codingFile1))))

#check
sum(file.exists(paste0(qidir, "annotations/coder2/",
                       na.omit(df.videos$codingFile2))))

#check
sum(file.exists(paste0(qidir, "annotations/coder3/",
                       na.omit(df.videos$codingFile3))))

```

# Export file list

```{r}
codebook_data <- df.videos %>%
  select(studyID, childID, videoID, n_coders, videoFileName, codingFile1, codingFile2, codingFile3, child.ageSessionRounded, child.gender, parent.race.nonwhite, video.privacy, consentnotes, usable, video.nTrialsExpected:video.actualDuration, which.dataset) %>%
  filter(n_coders>0)

codebook_data %>% write_tsv(paste0(qidir, "prephys_split0_videos.tsv"))
```

